On optimisation in HDR brachytherapy

### 2015-03-05 Paper BMT/article-sample-proceedings.tex
all of LP for today

\section{Linear Programming}
In Linear Programming a goal function and constraints are used to compute the optimal solution, as described in \citep{2}.

\subsection{Goal function and Constraints}
bla bla

\subsection{Results}
bla bla bla

>>>>

\section{Linear Programming}
In Linear Programming a objective function and constraints are used to compute the optimal solution, as described in \citep{2}.

\subsection{Objective function and Constraints}
The objective function sums up the dose for every organ at risk voxel and is then minimized. The constraints restrict the optimization so that the level of radiation in the tumor does not fall under a fixed value. The contraints can be relaxed to lower the level of radiation in the surrounding organs at the cost of lowering the radiation at the border of the tumor.

\subsection{Results}
bla bla bla
unsure bla bla
